Capstone Movielens Report

### 2025-12-07 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Micro fix for section: User+Movie+Genre+Year+Day Effect (UMGYDE) Model.

## User+Movie+Genre+Year+Day Effect (UMGYDE) Model
\
### Mathematical Description of the UMGYDE Model
\

If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYDE-model) describing the _UMGYDE Model_, for the current model, takes the form:

>>>>

## User+Movie+Genre+Year+Day Effect (UMGYDE) Model
\

### Mathematical Description of the UMGYDE Model
\

If we define $d_{i,j}$ as the _number of days since the earliest record_ in the `edx` dataset for movie $j$ rated by user $i$, then the formula \@ref(eq:UMGYE-model) describing the _UMGYDE Model_, for the current model, takes the form:
